Approximate Code: A Cost-Effective Erasure Coding Framework for Tiered Video Storage in Cloud Systems

### 2019-04-19 ApproximateCode.tex
version 3.8.1

\section{Approximate Code}\label{ApCode}
In this section, we introduce Approximate Code and its properties through a few simple examples.

\subsection{Overview of Approximate Code}
The construction of the Approximate Code is determined by 3 parameters $k$, $r$ and $h$. 
In a $n$-node array, $k$ of them are data nodes and $r=n-k$ nodes are for local parity, where each node can be divided into multiple blocks, and we label the number of blocks in a node as $s$.
Approximate Code are designed for $h$ arrays, therefore it includes $k*n$ data nodes and $r*h$ local parity nodes.
Besides them, $3-r$ nodes are designed for global parity, and the total number of nodes in Approximate Code ($k,r,h$) is $$h*(k+r) +3-r$$

\subsection{Framework Design}
The Approximate Code provides an erasure code framework for video storage in the cloud system. It uses an approximate strategy to split the erasure code scheme into two parts with different fault tolerances for application to important and minor data. It mainly includes two operations of coding segmentation and structure selection.

\begin{figure}[]
\centering
\includegraphics[width=\linewidth]{photo/Framework.pdf}
\caption{The framework of Approximate Code}
\label{fig-framework}
\end{figure}

\subsubsection{Code segmentation}
For any type of input erasure code, we assume that its fault tolerance is $x$. The Approximate Code first splits its parity block into two parts: local and global parity. The former verifies all important and non-critical data, while the latter only verifies important data. Code segmentation are designed to ensure that local parities can tolerate any $r$ node failures, so the fault tolerance of non-critical data is $r$. For important data, the code segmentation ensures that the parity block of important data can be completely recombined into the original $x$DFTs erasure code scheme.

\subsubsection{Structure selection}
The Approximate Code framework then choose the Structure for the input erasure code.
Approximate Code distribute important and unimportant data separately and mainly in two structure. As shown in Figure \ref{fig-ap-414}, in \emph{Structure 1}, important data occupies 1 of $s$ blocks in each node, and in \emph{Structure 2}, it occupies 1 of all $h$ data arrays.
We define that $h=s$, so in \emph{Structure 1} and \emph{Structure 2},important data accounts for $1/h$ of all data.

@@

@@

%As mentioned before, if it is considered that the nodes from the same column belong to the same node, this example includes 4 arrays with 7 nodes; otherwise, it includes 4 arrays with 22 nodes.

\begin{figure}[]
\centering
\includegraphics[width=\linewidth]{photo/AP-kmha-v7.pdf}
\caption{A sample of Approximate Codes $(4,1,4)$ in \emph{Structure 1}, and Approximate Code $(3,1,3)$ in \emph{Structure 2}.
Data nodes are marked as $N_i$, important data are marked as water green, local parity nodes are marked as orange and global parity nodes are marked as red.
}
\label{fig-ap-414}
\end{figure}

\begin{figure}[htb]
\centering
\includegraphics[width=0.45\textwidth]{photo/AP-RS-43.pdf}
\caption{The generate matrix of RS-based Approximate Codes $(4,1,4)$, where $ID_i$ and $UD_i$ represent the important and unimportant data in $N_i$. $G_0$ and $G_1$ are the parity blocks corresponding to important data blocks.}
\label{fig-ap-rs}
\end{figure}

>>>>

\begin{figure*}[ht!]
\centering
\includegraphics[width=\linewidth]{photo/Framework-v2.pdf}
\caption{The framework of Approximate Code}
\label{fig-framework}
\end{figure*}

\section{Approximate Code}\label{ApCode}
In this section, we introduce the Approximate Code Framework and its properties through a few simple examples.

\subsection{Overview of Approximate Code Framework}
The Approximate Code mainly includes three operations: code segmentation, structure selection and code generation, as shown in Figure \ref{fig-framework}.

\subsubsection{Code Segmentation}
For any type of input erasure code, we assume that its fault tolerance is $x$. The Approximate Code first splits its parity block into two parts: local and global. The former verifies all important and non-critical data, while the latter only verifies important data. Code segmentation are designed to ensure that local parities can tolerate any $r$ node failures, so the fault tolerance of non-critical data is $r$. For important data, the code segmentation ensures that the parity block of important data can be completely recombined into the original $x$DFTs erasure code scheme.

\subsubsection{Structure Selection}
The Approximate Code framework then choose the Structure for the input erasure code.
Approximate Code distribute important and unimportant data separately and mainly in two structure. As shown in Figure \ref{fig-ap-414}, in \emph{Structure 1}, important data occupies 1 of $s$ blocks in each node, and in \emph{Structure 2}, it occupies 1 of all $h$ data arrays.
We define that $h=s$, so in \emph{Structure 1} and \emph{Structure 2},important data accounts for $1/h$ of all data.

@@

\subsubsection{Code Generation}

The construction of the Approximate Code is determined by 3 parameters $k$, $r$ and $h$. 
In a $n$-node array, $k$ of them are data nodes and $r=n-k$ nodes are for local parity, where each node can be divided into multiple blocks, and we label the number of blocks in a node as $s$.
Approximate Code are designed for $h$ arrays, therefore it includes $k*n$ data nodes and $r*h$ local parity nodes.
Besides them, $3-r$ nodes are designed for global parity, and the total number of nodes in Approximate Code ($k,r,h$) is $$h*(k+r) +3-r$$

@@

%As mentioned before, if it is considered that the nodes from the same column belong to the same node, this example includes 4 arrays with 7 nodes; otherwise, it includes 4 arrays with 22 nodes.
\iffalse
\begin{figure}[]
\centering
\includegraphics[width=\linewidth]{photo/AP-kmha-v7.pdf}
\caption{A sample of Approximate Codes $(4,1,4)$ in \emph{Structure 1}, and Approximate Code $(3,1,3)$ in \emph{Structure 2}.
Data nodes are marked as $N_i$, important data are marked as water green, local parity nodes are marked as orange and global parity nodes are marked as red.
}
\label{fig-ap-414}
\end{figure}

\begin{figure}[htb]
\centering
\includegraphics[width=0.45\textwidth]{photo/AP-RS-43.pdf}
\caption{The generate matrix of RS-based Approximate Codes $(4,1,4)$, where $ID_i$ and $UD_i$ represent the important and unimportant data in $N_i$. $G_0$ and $G_1$ are the parity blocks corresponding to important data blocks.}
\label{fig-ap-rs}
\end{figure}
\fi
